SMT-Based Context-Bounded Model Checking for Embedded Systems: Challenges and Future Trends

### 2016-03-25 paper.tex
minor changes

\textbf{(RP2)} The SMT-based BMC approach proposed by Cordeiro and Fischer was further developed to verify correct lock acquisition ordering and the absence of deadlocks, data races, and atomicity violations in multi-threaded software based on POSIX and CUDA libraries~\cite{CordeiroF11,Pereira15}, considering monotonic partial-order reduction~\cite{KahlonWG09} and state-hashing techniques, in order to prune the state-space exploration~\cite{morse15}. Recent advances for verifying multi-threaded C programs have been proposed to speed up the verification time, which significantly prune the state-space exploration~\cite{Inverso14,civl15}. However, the class of concurrent programs ({\it e.g.}, CUDA, OpenCL, and MPI) that can be verified is still very limited. One possible research direction is to further extend BMC of multi-threaded C programs via Lazy Sequentialization~\cite{Inverso14}, in order to analyze unsatisfiability cores with the goal to remove redundant behaviour.

@@

%The authors would like to thank...
This research was supported by CNPq $475647$/$2013$-$0$ grant.

>>>>

\textbf{(RP2)} The SMT-based BMC approach proposed by Cordeiro, Fischer, and Marques-Silva was further developed to verify correct lock acquisition ordering and the absence of deadlocks, data races, and atomicity violations in multi-threaded software based on POSIX and CUDA libraries~\cite{CordeiroF11,Pereira15}, considering monotonic partial-order reduction~\cite{KahlonWG09} and state-hashing techniques, in order to prune the state-space exploration~\cite{morse15}. Recent advances for verifying multi-threaded C programs have been proposed to speed up the verification time, which significantly prune the state-space exploration~\cite{Inverso14,civl15}. However, the class of concurrent programs ({\it e.g.}, CUDA, OpenCL, and MPI) that can be verified is still very limited. One possible research direction is to further extend BMC of multi-threaded C programs via Lazy Sequentialization~\cite{Inverso14}, in order to analyze unsatisfiability cores with the goal to remove redundant behaviour.

@@

%The authors would like to thank...
The authors thank M. Dangl for reviewing a draft version of this paper.~This research was supported by CNPq $475647$/$2013$-$0$ grant.
